Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2019-11-04 04_Prep_data.Rmd
Added cluster grouping to the slim data

Warning this markdown file needs corrections to variable names.
Column headers for PM_MB_means were changed and the column names need to be corrected below accordingly

@@

>>>>

@@

```{r clustered_fungicide_applications}
source("R/slimming_PM_dat.R")
head(slim_PM_dat)

slim_PM_dat %<>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
  mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
  filter(!is.na(grain_yield.t.ha)) %>% 
  filter(!is.na(PM_final_severity))

```

```{r cluster}

slim_PM_dat %<>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 4 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>% 
  mutate(
    cluster_3 = case_when(
      fungicide_timing_3 < 14 ~ "Early",
      TRUE ~ "Recommended"
    )
  )

slim_PM_dat[slim_PM_dat$fungicide_ai == "control", c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
                                                     "cluster_1", "cluster_2","cluster_3")] <- "control"

```
